Why Donors Donate?

### 2020-09-19 analysis/05_market_simulator.Rmd
Revert "testing matrix multiplication to find issue with market shres not lining up with excel sheet. Also made capitalization consistent in inputs"
This reverts commit cab2c11df4e85d3fae0681ce339f458b47698cf9.

test_beta <- as.data.frame(matrix(rep(0), nrow = 12))

test_beta$levels = c("Persona 1", "Persona 2", "Persona 3", "input1", "input2", "input3", "input4", "input5", "input6", "input7", "input8", "input9")

# Persona Reactive Element

test_beta$p1 <- 0
test_beta$p1[1] <- 1

test_beta$p2 <- 0
test_beta$p2[2] <- 1

test_beta$p3 <- 0
test_beta$p3[3] <- 1

test1 <- test_beta[,3]

@@

selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"),
         selected = "Some college",
         width = "450px")

@@

selectInput("p2_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE,
         selected = 'American Indian or Alaska Native',
         width = "450px")

@@

selectInput("p3_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other (Gender)"),
         selected = "Female",
         width = "450px")

@@

selectInput("p3_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"),
         selected = "Graduate or professional degree",
         width = "450px")

@@

selectInput("p3_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE,
         selected = c("Black or African American",'American Indian or Alaska Native'),
         width = "450px")

@@

textInput("ai_id",
          label = "Organization name",
          value = "Organization 1",
          placeholder = "Enter organization name",
          width = "450px")

selectInput("org1_id",
            label = "Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross",
            width = "450px")

selectInput("ai_issue", 
            label = "Issue area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Emergency response",
            width = "450px")

selectInput("ai_fin_trans",
            label = "Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency",
            width = "450px")

selectInput("ai_account",
            label = "Financial accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability",
            width = "450px")

selectInput("ai_funding",
            label = "Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"),
            selected = "Many small private donations",
            width = "450px")

selectInput("ai_gov_relat",
            label = "Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"),
            selected = "Friendly relationship with government",
            width = "450px")

@@

textInput("gp_id",
          label = "Organization name",
          value = "Organization 2",
          placeholder = "Enter organization name",
          width = "450px")

selectInput("org2_id",
            label = "Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross",
            width = "450px")

selectInput("gp_issue", 
            label = "Issue area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Environment",
            width = "450px")

selectInput("gp_fin_trans",
            label = "Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency",
            width = "450px")

selectInput("gp_account",
            label = "Financial accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability",
            width = "450px")

selectInput("gp_funding",
            label = "Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"),
            selected = "Many small private donations",
            width = "450px")

selectInput("gp_gov_relat",
            label = "Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"),
            selected = "Friendly relationship with government",
            width = "450px")

@@

textInput("ox_id",
          label = "Organization name",
          value = "Organization 3",
          placeholder = "Enter organization name",
          width = "450px")

selectInput("org3_id",
            label = "Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross",
            width = "450px")

selectInput("ox_issue", 
            label = "Issue area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Human rights",
            width = "450px")

selectInput("ox_fin_trans",
            label = "Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency",
            width = "450px")

selectInput("ox_account",
            label = "Financial accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability",
            width = "450px")

selectInput("ox_funding",
            label = "Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"),
            selected = "Many small private donations",
            width = "450px")

selectInput("ox_gov_relat",
            label = "Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"),
            selected = "Friendly relationship with government",
            width = "450px")

@@

textInput("rc_id",
          label = "Organization name",
          value = "Organization 4",
          placeholder = "Enter organization name",
          width = "450px")

selectInput("org4_id",
            label = "Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross",
            width = "450px")

selectInput("rc_issue", 
            label = "Issue area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Refugee relief",
            width = "450px")

selectInput("rc_fin_trans",
            label = "Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency",
            width = "450px")

selectInput("rc_account",
            label = "Financial accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability",
            width = "450px")

selectInput("rc_funding",
            label = "Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"),
            selected = "Many small private donations",
            width = "450px")

selectInput("rc_gov_relat",
            label = "Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"),
            selected = "Friendly relationship with government",
            width = "450px")

>>>>

# beta_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))
# 
# beta_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
# 
# 
# 
# # Persona Reactive Element
# 
# beta_persona_test$p1 <- 1
# 
# beta_persona_test$p2 <- 2
# 
# beta_persona_test$p3 <- 3
#         
# persona1 <- persona_data[,2]
# 
# p_beta1 <- as.matrix(public_political_social_charity_demo) %*%   
#   
#   as.matrix(persona1) %*% beta_persona_test[,3]

@@

selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"),
         selected = "2 year degree",
         width = "450px")

@@

selectInput("p2_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE,
         selected = "White",
         width = "450px")

@@

selectInput("p3_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other (Gender)"),
         selected = "Male",
         width = "450px")

@@

selectInput("p3_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"),
         selected = "2 year degree",
         width = "450px")

@@

selectInput("p3_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE,
         selected = "White",
         width = "450px")

@@

textInput("ai_id",
          label = "Organization Name",
          value = "Organization 1",
          placeholder = "Enter Organization Name",
          width = "450px")

selectInput("org1_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross",
            width = "450px")

selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Emergency response",
            width = "450px")

selectInput("ai_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency",
            width = "450px")

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability",
            width = "450px")

selectInput("ai_funding",
            label = "Select Funding Source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"),
            width = "450px")

selectInput("ai_gov_relat",
            label = "Select Relationship With Host Government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"),
            width = "450px")

@@

textInput("gp_id",
          label = "Organization Name",
          value = "Organization 2",
          placeholder = "Enter Organiation Name",
          width = "450px")

selectInput("org2_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross",
            width = "450px")

selectInput("gp_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Environment",
            width = "450px")

selectInput("gp_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency",
            width = "450px")

selectInput("gp_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability",
            width = "450px")

selectInput("gp_funding",
            label = "Select Funding Source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"),
            width = "450px")

selectInput("gp_gov_relat",
            label = "Select Relationship With Host Government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"),
            width = "450px")
```

@@

textInput("ox_id",
          label = "Organization Name",
          value = "Organization 3",
          placeholder = "Enter Organiation Name",
          width = "450px")

selectInput("org3_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross",
            width = "450px")

selectInput("ox_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Human rights",
            width = "450px")

selectInput("ox_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency",
            width = "450px")

selectInput("ox_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability",
            width = "450px")

selectInput("ox_funding",
            label = "Select Funding Source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"),
            width = "450px")

selectInput("ox_gov_relat",
            label = "Select Relationship With Host Government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"),
            width = "450px")
```

@@

textInput("rc_id",
          label = "Organization Name",
          value = "Organization 4",
          placeholder = "Enter Organiation Name",
          width = "450px")

selectInput("org4_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"),
            selected = "Red Cross",
            width = "450px")

selectInput("rc_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            selected = "Refugee relief",
            width = "450px")

selectInput("rc_fin_trans",
            label = "Select Financial Transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            selected = "Engages in transparency",
            width = "450px")

selectInput("rc_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"),
            selected = "Engages in accountability",
            width = "450px")

selectInput("rc_funding",
            label = "Select Funding Source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government grants"),
            width = "450px")

selectInput("rc_gov_relat",
            label = "Select Relationship With Host Government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"),
            width = "450px")
```
